---
title: "Assignment Three for Lab3"
author: "Taehoon Ha"
date: "09/28/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(gapminder)
library(tidyverse)
library(ggrepel)
data("gapminder")
```

### 1. Read Chapter 19 from "R for data science" (online version).

### 2. Create a GitHub repository Lab3 (ï¬les with R code for the assignment should be added to this repository)

### 3. Complete Problem 2 from "Activity for Lab 3".
  * Load gapminder data.
  * Create a plot for 2007 year data only: GDP per capita vs. life expectancy
  * Annotate european countries with "GDP per capita > 40000"
```{r}
temp <- gapminder %>%
  filter(year == 2007) %>%
  select(country, continent, gdpPercap, lifeExp)

temp2 <- temp %>%
  filter(continent == 'Europe', gdpPercap > 40000)

temp %>%
  ggplot(aes(x = gdpPercap, y = lifeExp)) + 
  geom_point() +
  theme_bw() +
  labs(x = "GDP per capita", y = "life expectancy") +
  geom_text_repel(data = temp2,
                  label = temp2$country,
                  color = 'blue',
                  force = 0,
                  nudge_y = -1)
```

### 4. Modify your R code for the previous problem and recreate the graph:
```{r}
temp %>%
  ggplot(aes(x = gdpPercap, y = lifeExp)) + 
  geom_point(shape = 1, size = 2, stroke = 1.5) +
  theme_bw() +
  labs(x = "GDP per capita", y = "life expectancy") +
  annotate("rect", 
           xmin = 39000, xmax = 51000,
           ymin = 75, ymax = 85,
           alpha = .25, fill = 'red') +
  annotate("text", 
           x = 45000, y = 72.5, 
           label = "Countries with\nhighest GDP",
           size = 4, fontface = 2)
```