---
title: "Activity Three for Lab3"
author: "Taehoon Ha"
date: "09/26/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd('/Users/taehoonh/github')
```

```{r}
library(ggplot2)
library(gapminder)
library(tidyverse)
library(ggrepel)
data("gapminder")
```

### Problem 1
In lecture 3 notes a density plot of a normally distributed random variable with area under the curve was created using base R graphics:
```{r}
curve(dnorm, from = -4, to = 4, ylab = "PDF", main = "Pr(X <= -1)")
coord.x = c(-4, seq(-4,-1, by=0.1), -1)
coord.y = c(0, dnorm(seq(-4, -1, by=0.1)), 0)
polygon(coord.x, coord.y, col = 2)
```

Write R code using ggplot2 to recreate the density plot with area under the curve.
```{r}
x <- seq(-4, 4, 0.1)

ggplot(data = NULL, aes(x = x, y = dnorm(x))) +
  geom_line() +
  geom_polygon(data = NULL,
               aes(x = c(-4,seq(-4,-1, by=0.1),-1),
                   y = c(0,dnorm(seq(-4,-1, by=0.1)), 0)),
               fill = "red", col = 'black') +
  labs(x = "X", y = "Density", title = "Pr(X <= −1)") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))
```

### Problem 2
  * Load gapminder data.
  * Create a plot for 2007 year data only: "GDP per capita" vs. "Life expectancy"
  * Annotate european countries with "GDP per capita" > 40000

#### 1) Using geom_text()
```{r}
temp <- gapminder %>%
  filter(year == 2007) %>%
  select(country, continent, gdpPercap, lifeExp)

temp2 <- temp %>%
  filter(continent == 'Europe', gdpPercap > 40000)

temp %>% ggplot(aes(x=gdpPercap, y=lifeExp)) + 
  geom_point() +
  theme_bw() +
  labs(x = "GDP per capita", y = "life expectancy") +
  geom_text(data = temp2,
            aes(x = gdpPercap, y = lifeExp, label = country),
            color = 'blue',
            nudge_y = -1)
```
  
#### 2) Using geom_text_reple()
```{r}
temp <- gapminder %>%
  filter(year == 2007) %>%
  select(country, continent, gdpPercap, lifeExp)

temp2 <- temp %>%
  filter(continent == 'Europe', gdpPercap > 40000)

temp %>%
  ggplot(aes(x = gdpPercap, y = lifeExp)) + 
  geom_point() +
  theme_bw() +
  labs(x = "GDP per capita", y = "life expectancy") +
  geom_text_repel(data = temp2,
                  label = temp2$country,
                  color = 'blue',
                  force = 0,
                  nudge_y = -1)
```